Price of Anarchy for Mean Field Games

### 2018-07-23 PoA.tex

% proposition b2 bar
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$
	then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t>0.$$
	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$

   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure. Thus, from Proposition \ref{prop:diff_SC}, and by the bounded convergence theorem, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0. $$
	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
	\begin{equation*}
	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.     
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$

@@

% comment out: error in using Mean Value theorem	
\begin{comment}
	-----------------

	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$. We previously showed that $\lim_{\bar{b}_2 \to \infty}h(\bar{b}_2)= c_3 >0$. Let $\epsilon_1>0$ such that $c_3 - 2 \epsilon_1 >0$. Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\left\vert h(\bar{b}_2) - c_3 \right\vert < \epsilon_1$. Then $h(\bar{b}_2) - c_3 + 2\epsilon_1 > \epsilon_1$ and 
	\begin{equation*}
	\begin{array}{rl}
	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{1/2} h(\bar{b}_2) }  & 	\displaystyle  = e^{- \kappa (b_2 + \bar{b}_2)^{1/2} (h(\bar{b}_2) - c_3 + 2\epsilon_1 )}\cdot e^{- \kappa  (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} +  \ln (b_2 + \bar{b}_2) } \\
		&	\displaystyle  \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{1/2} \epsilon_1 } \cdot \exp \left( - \kappa (c_3 - 2 \epsilon_1 ) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)\right) \\
		%& 	\displaystyle  = c_5 e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} + \ln (b_2 + \bar{b}_2)} \\
		%& \xrightarrow[\bar{b}_2 \to \infty]{}0.
	\end{array}
	\end{equation*}
	The first term on the right hand side of the above inequality is a constant depending only on $\epsilon_1$, and the second term tends towards $0$ when $b_2 \to \infty$. Thus,  for any $\epsilon>0$, there exists a $\bar{b}_2^{*,2} \geq \bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$ we have:
	\begin{equation}
	|(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) }|<\epsilon.
	\label{eq:limit_p_f(p)}
	\end{equation}

 	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$. Given $\epsilon>0$, there exists a $\bar{b}_2^{*,3} \geq 1$ such that for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq c_3 + \epsilon$. Thus, for any $\bar{b}_2 > \bar{b}_2^{*,3} \geq 1$ we deduce:
 	$$ \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq \frac{c_3+ \epsilon}{(b_2 + \bar{b}^{*,3}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
 	$$

 	\begin{comment}	
 	Idem, we can show that for $t_1 \in [0,T)$:
	\begin{equation*}
	\begin{split}
	(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T- t_1)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t_1)} }\\
	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w} =: c_4 >0,
	\end{split}
	\end{equation*}
	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$.

	Idem we can show that for any $t_1 \in [0,T)$:
	\begin{equation*}
		(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} \xrightarrow[\bar{b}_2 \to \infty]{} (r+ \bar{r}(1-\bar{s})^2) c_{\delta_w^{\bar{b}_2 \to \infty}} =: c_4, \qquad \text{where } \quad c_{\delta_w^{\bar{b}_2 \to \infty}} = \sqrt{\frac{q+ \bar{q}(1-s)^2}{r + \bar{r}(1 - \bar{s})^2} }.
	\end{equation*}
	Thus, $\left\vert w_{t_1}^{\bar{b}_2} \right\vert $ can also be bounded by $c_4 + \epsilon$ for any $\bar{b}_2$ large enough.

	Hence, together with equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 > \bar{b}_2^*$ we have
	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon^2.$$
	Thus, by taking $\epsilon \to 0$, we have:
	$$\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.$$
\end{comment}

@@

\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, $Var(\xi)>0$, and $\lambda \neq 1$, then
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
	\begin{split}
		\left|u^{b_1}_t\right| &\leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		&\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon}\\
		&=:c,
	\end{split}
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. By the assumption on $\lambda$, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{b_1\to 0}\bar{x}_t^{MFG,b_1} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{MFG,b_1\to 0}>0.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,b_1\to 0}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$

@@

    Now we consider $b_1 \to \infty$. For each $b_1>0$, we have the following bounds over $t\in[0,T]$:
    \begin{equation*}
    \begin{split}
	    \left| u^{b_1}_t\right| &\leq \frac{C^u+D^u(\delta^{+,b_1}_u-\delta^{-,b_1}_u)}{-\delta^{-,b_1}_u}=:h_u(b_1) \\
		\left| w^{b_1}_t\right| &\leq \frac{C^w+D^w(\delta^{+,b_1}_w-\delta^{-,b_1}_w)}{-\delta^{-,b_1}_w}=:h_w(b_1) \\
		\left| \eta^{b_1}_t\right| &\leq \frac{C^{\eta}+D^{\eta}(\delta^{+,b_1}_{\eta}-\delta^{-,b_1}_{\eta})}{-\delta^{-,b_1}_{\eta}}=:h_{\eta}(b_1) \\
		\left| \bar{x}^{MFG,b_1}_t \right| &\leq \left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)}=:h_{\bar{x}}(b_1).
    \end{split}
    \end{equation*}
    Thus, from Proposition \ref{prop:diff_SC}, we have:
    \begin{equation*}
	    \Delta SC^{b_1} \leq \frac{1}{2}BT(h_u(b_1)+h_w(b_1))^2 (h_{\bar{x}}(b_1))^2.
    \end{equation*}

    We also have the following lower bound:
    \begin{equation*}
	\begin{split}
	SC^{MKV,b_1} &\geq \frac{1}{2}(q_T+\bar{q}_T)v^{b_1}_T \\
	& \geq (q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
	\end{split}
    \end{equation*}
    Let $h(b_1)=\max \{h_u(b_1),h_w(b_1),h_{\eta}(b_1) \}$. It is easy to check that $\lim_{b_1 \to \infty}h(b_1)=\infty$. Combining the above bounds and using the assumption $Var(\xi)>0$, we have:
    \begin{equation*}
    \begin{split}
	    \frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}&\leq \frac{2BT(h(b_1))^2 (h_{\bar{x}}(b_1))^2}{\frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BT(h(b_1))^2 (\left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)})^2}{(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BTe^{2T(\bar{b}_1)}(\mathbb{E}(\xi))^2  }{(q_T+\bar{q}_T)Var(\xi)} \cdot \frac{(h(b_1))^2}{e^{-2TB^{\eta}h(b_1))}}\\
	    &\xrightarrow[b_1 \to \infty ]{} 0.
    \end{split}
    \end{equation*}
    Therefore,
    \begin{equation*}
	    \lim_{b_1 \to \infty}\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}=0,
    \end{equation*}
    and thus, $\lim_{b_1 \to \infty} PoA^{b_1}=1$. ToDo: last case.

>>>>

% proposition b2 bar
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$, then:
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$. From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t\neq 0.$$
	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$

   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure. Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0. $$
	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
	\begin{equation*}
	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.     
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$

@@

@@

\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), $b_1>0$, $\bar{b}_1>0$, the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
	\begin{split}
		\left|u^{b_1}_t\right| &\leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		&\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon}\\
		&=:c,
	\end{split}
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. By our assumption on $\bar{b}_1$, we have $A^{u,b_1\to 0} \neq A^{w,b_1\to 0}$ and thus, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{b_1\to 0}\bar{x}_t^{MFG,b_1} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{MFG,b_1\to 0}\neq 0.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,b_1\to 0}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$

@@

    Now we consider $b_1 \to \infty$. For each $b_1>0$, we have the following bounds over $t\in[0,T]$:
    \begin{equation*}
    \begin{split}
	    \left| u^{b_1}_t\right| &\leq \frac{C^u+D^u(\delta^{+,b_1}_u-\delta^{-,b_1}_u)}{-\delta^{-,b_1}_u}=:h_u(b_1) \\
		\left| w^{b_1}_t\right| &\leq \frac{C^w+D^w(\delta^{+,b_1}_w-\delta^{-,b_1}_w)}{-\delta^{-,b_1}_w}=:h_w(b_1) \\
		\left| \eta^{b_1}_t\right| &\leq \frac{C^{\eta}+D^{\eta}(\delta^{+,b_1}_{\eta}-\delta^{-,b_1}_{\eta})}{-\delta^{-,b_1}_{\eta}}=:h_{\eta}(b_1) \\
		\left| \bar{x}^{MFG,b_1}_t \right| &\leq \left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)}=:h_{\bar{x}}(b_1).
    \end{split}
    \end{equation*}
    Thus, from Proposition \ref{prop:diff_SC}, we have:
    \begin{equation*}
	    \Delta SC^{b_1} \leq \frac{1}{2}BT(h_u(b_1)+h_w(b_1))^2 (h_{\bar{x}}(b_1))^2.
    \end{equation*}
    We also have the following lower bound:
    \begin{equation*}
	\begin{split}
	SC^{MKV,b_1} &\geq \frac{1}{2}(q_T+\bar{q}_T)v^{b_1}_T \\
	& \geq \frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
	\end{split}
    \end{equation*}

    Let $h(b_1)=\max \{h_u(b_1),h_w(b_1),h_{\eta}(b_1) \}$. Since $\lim_{b_1 \to \infty} |A^{u,b_1}|=\infty$, we have:
    \begin{equation*}
    \begin{split}
	    \delta^{+,b_1}_u-\delta^{-,b_1}_u&=2 \sqrt{(A^{u,b_1})^2+BC^u} \\
	    &\xrightarrow[b_1 \to \infty]{}\infty,
    \end{split}
    \end{equation*}
    and
    \begin{equation*}
    \begin{split}
    -\delta^{-,b_1}_u&=A^{u,b_1}+\sqrt{(A^{u,b_1})^2+BC^u} \\
    &\xrightarrow[b_1 \to \infty]{}0.
    \end{split}
    \end{equation*}    
    Thus, $\lim_{b_1 \to \infty}h_u(b_1)=\infty$, which implies $\lim_{b_1 \to \infty}h(b_1)=\infty$. Combining the above bounds and using the assumption $Var(\xi)>0$, we have:

    \begin{equation*}
    \begin{split}
	    \frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}&\leq \frac{2BT(h(b_1))^2 (h_{\bar{x}}(b_1))^2}{\frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BT(h(b_1))^2 (\left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)})^2}{(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BTe^{2T(\bar{b}_1)}(\mathbb{E}(\xi))^2  }{(q_T+\bar{q}_T)Var(\xi)} \cdot \frac{(h(b_1))^2}{e^{-2TB^{\eta}h(b_1))}}\\
	    &\xrightarrow[b_1 \to \infty ]{} 0.
    \end{split}
    \end{equation*}
    Therefore,
    \begin{equation*}
	    \lim_{b_1 \to \infty}\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}=0,
    \end{equation*}
    and thus, $\lim_{b_1 \to \infty} PoA^{b_1}=1$. ToDo: last case.
